A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-07-13 paper/project.tex
Fixed low res version of single-rod and work on project text

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/entropy-1D}
\end{center}
\caption{ Entropy for a slab of water with molecules constrained to move in one 
dimension. \textcolor{red}{FIX UNITS}}
\label{fig:entropy-1D}
\end{figure}

@@

@@

>>>>

One of the most computationally simple ways to study confined water is by
constraining it to a slit where the water molecules can only move in one
dimension. We apply a constraining potential of the form

\begin{align}
V = n_l*constraint + 100*n_v (FIXME)
\end{align}

such that the density is 100 times the vapor density outside the slit 
and approximately equal to the saturated liquid density inside. The slits
range in size from 5 bohrs to 150 bohrs (FIX - redo in nm?). We 
minimize the energy and calculate density, energy, and $X$ on a lattice
with a spacing of 0.2 bohrs between data points.

The density profile for a slit of size 60 bohrs is shown in Figure 
\ref{fig:density-1D}. Near the interface, there are oscillations around the 
liquid density which decrease near the center of the slit. We expect the
center of the slit to act approximately like bulk water, and the absence 
of oscillations supports this. For larger slits (~120 bohrs or more) the
majority of the water molecules in the slit act like the bulk. We also 
determine the smallest slit that can contain liquid water, approximately 
30 bohrs. For smaller slits, the initial liquid water inside will vaporize.

@@

The value of $X$ behaves as expected for water constrained to a slit. We
show in Figure \ref{fig:xassoc-1D} the plot of $X$ for a slit of 60 bohrs.
Outside the slit, there is no hydrogen bonding, and inside $X$ is 
approximately equal to
that of saturated liquid water.

@@

We move into two dimensions by studying a single hydrophobic rod
immersed in water.

@@

(Plot with low (0.4 bohrs), regular (0.2), and high (0.05) resolution 
for single rod.)
